---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# radous

<!-- badges: start -->
[![R build status](https://github.com/feddelegrand7/radous/workflows/R-CMD-check/badge.svg)](https://github.com/feddelegrand7/radous/actions)
<!-- badges: end -->

`radous` allows you to generate random user data from the [Random User Generator API](https://randomuser.me/) which can be useful in many situations : 

- Teaching;
- Testing a function; 
- Testing an application (Shiny, Dash or others)

You can generate up to 5000 observations in one query.


## Installation

You can install the development version of `radous` from [GitHub](https://github.com/) with:

```{r, eval=FALSE}

#install.packages("remotes") ---- If not installed

remotes::install_github("feddelegrand7/radous")


```


## Usage

`radous` is extremely simple to use and has one function: `get_data()`.

Suppose we want to generate 10 random user data: 


```{r}

library(radous)

get_data(n = 10)

```

If you want to generate always the same set of users, you can use the `seed` argument: 


```{r}

get_data(n = 5, seed = "1990")

```


Let's run the above code again to check if we get the same info: 

```{r}

get_data(n = 5, seed = "1990")

```

If you need some user images, it's easy to get: 

```{r, message=FALSE, warning=FALSE}

library(dplyr)

random_image <- get_data(n = 1) %>% select(picture_large) %>% pull()

htmltools::img(src = random_image, height = "150px", width = "150px")


```


## Teaching with `radous` 

The generated data has 34 variables (columns) with different types of information that you can play with. The data frame is particularly suited for teaching the tidyverse, here some examples: 

#### Select 


> Here we select columns that are related to users' location:


```{r message=FALSE, warning=FALSE}

library(tidyverse)


df <- get_data(n = 500, seed = 123)


df %>% select(contains("location"))



```





#### Filter 


> Getting the users that are US citizens:


```{r message=FALSE, warning=FALSE}



df %>% filter(nat == "US")

```


#### relocate 


> Relocating the last column `nat` to the beginning: 

```{r}

df %>% relocate(nat, before = gender)

```

#### group_by & summarise


> Calculating median age by gender:


```{r}

df %>% group_by(gender) %>% 
  summarise(median_age = median(dob_age))



```
#### count, arrange & desc


> Getting the number of users per country of residence:

```{r}

df %>% 
  count(location_country) %>% 
  arrange(desc(n))



```


## Code of Conduct

Please note that the radous project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
